SVG: The Paper

### 2022-11-01 Analysis/index_revisions_2.Rmd
getting ready for resubmission

```{r}
# set ggplot2 options
#theme_set(ggthemes::theme_tufte() + 
#            theme(plot.background = element_rect(fill = "#fffff8", colour = "#fffff8")))

# for saving graphs for paper
theme_set(ggthemes::theme_tufte(base_size = 16) + 
            theme(plot.background = element_rect(fill = "#ffffff", colour = "#ffffff")))

@@

ggsave("../Figures/qjep_preds.pdf", 
       plt_b2 / (plt1 + plt2) + 
       plot_layout(guides = "collect") & theme(legend.position = 'bottom'),
       width = 10, height = 10)

@@

ggsave("../Figures/qjep_indiv_diff.pdf", 
       plt_a + plt_b + 
         plot_layout(widths = c(1, 2)), width = 12, height = 4)
```

@@

ggsave("../Figures/trial_time.png", plt + theme_bw() + theme(legend.position = "none"), width = 4, height = 6)

@@

ggsave("../Figures/targ_time.png", width = 7, height = 4)

@@

create_post_plot("x") + create_post_plot("y") + plt_mu #& theme_bw()
ggsave("../Figures/init_sel_mdl.pdf", width = 10, height = 3.5)
```

@@

ggsave("../Figures/qjep_init_sel_preds.pdf",
       width = 8, height = 4)

>>>>

```{r}
# set ggplot2 options
theme_set(ggthemes::theme_tufte() + 
            theme(plot.background = element_rect(fill = "#fffff8", colour = "#fffff8")))

# for saving graphs for paper
#theme_set(ggthemes::theme_tufte(base_size = 16) + 
#            theme(plot.background = element_rect(fill = "#ffffff", colour = "#ffffff")))

@@

#ggsave("../Figures/qjep_preds.pdf", 
#       plt_b2 / (plt1 + plt2) + 
#       plot_layout(guides = "collect") & theme(legend.position = 'bottom'),
#       width = 10, height = 10)

@@

#ggsave("../Figures/qjep_indiv_diff.pdf", 
#       plt_a + plt_b + 
#         plot_layout(widths = c(1, 2)), width = 12, height = 4)
```

@@

#ggsave("../Figures/trial_time.png", plt + theme_bw() + theme(legend.position = "none"), width = 4, height = 6)

@@

#ggsave("../Figures/targ_time.png", width = 7, height = 4)

@@

create_post_plot("x") + create_post_plot("y") + plt_mu #& theme_bw()
#ggsave("../Figures/init_sel_mdl.pdf", width = 10, height = 3.5)
```

@@

#ggsave("../Figures/qjep_init_sel_preds.pdf",
#       width = 8, height = 4)
